Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-26 paper/agree-semantics.tex
declutter defs for Once and Since; minot yidying

The temporal operators deal with time in more significant ways. The
value of $\konst{pre}(e)$ at time $t$ is the value of $e$ at time
$t-1$ (at time zero, \konst{pre} is undefined).  
A followed-by, $e_1 \to e_2$, evaluates to $e_1$ at time 0; otherwise it is $e_2$.
Followed-by is often used to give a value to a stream in the first step so that subsequent steps are able to use $\konst{pre}(e)$.
\[
\begin{array}{rcl}
\sem{\konst{pre}(e)}^E_t & = & \sem{e}^E_{t-1}, \mathrm{when}\ t > 0 \\
\sem{e_1 \to e_2}^E_t & = & \itelse{t=0}{\sem{e_1}^E_0}{\sem{e_2}^E_t} \\
\sem{\konst{Hist}(b)}^E_t & = & \forall n \leq t.\; \sem{b}^E_n
\end{array}
\]

Although basic, these definitions can be used to define higher-level
past-time operators from PLTL such as \konst{Once} and \konst{Since}.
These are defined relative to their corresponding bound output stream $o$.
\[
   \begin{array}{rcl}
      \sem{\konst{Once}(b)}^E_t & = & \sem{b \vee (\mathit{false} \to \konst{pre}(o))}^E_t \\
      \sem{\konst{Since}(a, b)}^E_t & = & \sem{b \vee (a and (\mathit{false} \to \konst{pre}(o)))}^E_t \\
   \end{array}
\]
$\konst{Once}(b)$ is true if $b$ has ever been true before, or in, the current moment.
$\konst{Since}(a, b)$ is true if $a$ has been true in all moments up to the present one since $b$ most recently became true.
These both refer the their bound output stream $o$ to know if they were true or false in their previous step.
All other past-time operators of PLTL can be defined similarly.

>>>>

The temporal operators deal with time in more significant ways. The
value of $\konst{pre}(e)$ at time $t$ is the value of $e$ at time
$t-1$ (at time zero, \konst{pre} is undefined).
A followed-by, $e_1 \to e_2$, evaluates to $e_1$ at time zero; otherwise it is $e_2$.
Followed-by is often used to give a value to a stream in the first step so that subsequent steps are able to use $\konst{pre}(e)$.
\[
\begin{array}{rcl}
\sem{\konst{pre}(e)}^E_t & = & \sem{e}^E_{t-1}, \mathrm{when}\ t > 0 \\
\sem{e_1 \to e_2}^E_t & = & \itelse{t=0}{\sem{e_1}^E_0}{\sem{e_2}^E_t} \\
\sem{\konst{Hist}(b)}^E_t & = & \forall n \leq t.\; \sem{b}^E_n
\end{array}
\]

Although basic, these definitions can be used to define higher-level
past-time operators from PLTL such as \konst{Once} and \konst{Since}.
These can be expressed in a recursive style as follows:
%% \[
%%    \begin{array}{rcl}
%%       \sem{\konst{Once}(b)}^E_t & = & \sem{b \vee (\konst{false} \to \konst{pre}(o))}^E_t \\
%%       \sem{\konst{Since}(a, b)}^E_t & = & \sem{b \vee (a and (\konst{false} \to \konst{pre}(o)))}^E_t \\
%%    \end{array}
%% \]
\[
\begin{array}{rcl}
 \konst{Once}(b) & = & b \vee \konst{pre}(\konst{Once}(b)) \\
 \konst{Since}(a, b) & = & b \lor (a \land \konst{pre}(\konst{Since}(a, b))
   \end{array}
\]

$\konst{Once}(b)$ is true if $b$ has ever been true before, or in, the
current moment.  $\konst{Since}(a, b)$ is true if $a$ has been true in
all moments up to the present one since $b$ most recently became true.
All other past-time operators of PLTL can be defined similarly.
